### 2015-11-24 Manuscript/BiologyLetters/CoverLetter.tex
Cover letter update

Our research article, entitled ``Assessment of cladistic data availability for living mammals'', is to our knowledge, the first to thoroughly assess the availability of cladistic (morphological) data in living mammals.
Additionally, we test whether the available data in each mammalian order is randomly distributed or clustered towards certain clades to investigate whether the placement of fossil taxa within these order would have respectively non \textit{a priori} bias or would be bias towards the clades with the most data.

Our results show that, unfortunately 22 of 28 mammalian orders have less than 25\% species with available morphological data.
Fortunately, however, most of this available data was randomly distributed across each mammalian order expect for 6 for which the data was biased towards certain clades.
We hope that our work will encourage cladisticians %TG: or is that how there are called?
to sample more data for living species and thus serving as a stepping stone for improving combining living and fossil taxa in the same phylogenies.

>>>>

Our research article, entitled ``Assessment of cladistic data availability for living mammals'', is to our knowledge, the first to thoroughly assess the availability of cladistic (morphological) data in living mammals.
Additionally, we test whether the available data in each mammalian order is randomly distributed or clustered towards certain clades to investigate whether the placement of fossil taxa within these order would have respectively no \textit{a priori} bias or would be biased towards the clades with the most data.

Our results show that 22 of 28 mammalian orders have less than 25\% species with available morphological data.
Fortunately, however, most of this available data was randomly distributed across each mammalian order expect for 6 for which the data was biased towards certain clades.
We hope that our work will encourage cladisticians %TG: or is that how there are called?
to sample more data for living species and thus serving as a stepping stone for improving combining living and fossil taxa in the same phylogenies.
